Weighted Model Counting with Conditional Measures

### 2020-07-25 paper.tex
Make the paper 5% more readable

\section{Preliminaries}

\begin{itemize}
\item Make up my mind about $a, b$ vs. $x, y$ and stick to it (maybe $x, y$?).
\item Terminology: `with generating set $S$' $\to$ `over $S$'.
\item Notation: if $L$ denotes literals, then it doesn't denote a generating
  set. Literals should be $U$.
\item Describe the parallel between BAs and powersets.
\item Describe \cref{tbl:notation_example} as an example. We will use
  set-theoretic notation for $2^U$ and Boolean-algebraic notation for $2^{2^U}$
  (except for atoms).
\end{itemize}

@@

Consider the Boolean algebra $(2^{2^U}, \land, \lor, \neg, \bot, \top)$. A
partial order $\le$ on $2^{2^U}$ is defined by $a \le b$ if $a = b \land a$ (or,
equivalently, $a \lor b = b$) for all $a, b \in 2^{2^U}$.

\begin{definition}[\cite{DBLP:books/daglib/0090259,levasseur2012applied}]
  An element $a \ne 0$ of $2^{2^U}$ is an \emph{atom} if, for all $x \in
  2^{2^U}$, either $x \land a = a$ or $x \land a = 0$. Equivalently, $a \ne 0$
  is an atom if there is no $x \in \mathbf{B}$ such that $0 < x < a$.
  Equivalently, $a \ne 0$ is an atom if $|a| = 1$, i.e., $a = \{ u \}$ for some
  $u \in 2^U$ (this is how we will denote atoms in the remainder of the paper).
  Note that atoms in Boolean algebras correspond to models.
\end{definition}

\begin{lemma}[\cite{givant2008introduction}] \label{thm:representation}
  The following are equivalent:
  \begin{itemize}
  \item $\mathbf{B}$ is atomic.
  \item For any $x \in \mathbf{B}$, $x = \bigvee_{\text{atoms } a \le x} a$.
  \item $1$ is the supremum of all atoms.
  \end{itemize}
\end{lemma}

\begin{definition}[\cite{gaifman1964concerning,DBLP:books/daglib/0090259}] \label{def:measure}
  A \emph{measure} on $\mathbf{B}$ is a function $m\colon
  \mathbf{B} \to \mathbb{R}_{\ge 0}$ such that:
  \begin{itemize}
  \item $m(0) = 0$;
  \item $m(a \lor b) = m(a) + m(b)$ for all $a, b \in \mathbf{B}$ whenever $a
    \land b = 0$.
  \end{itemize}
  If $m(1) = 1$, we call $m$ a \emph{probability measure}. Also, if $m(x) > 0$
  for all $x \ne 0$, then $m$ is \emph{strictly positive}.
\end{definition}

\begin{lemma}[\cite{sikorski1969boolean}] \label{lemma:order}
  For any $a, b \in \mathbf{B}$, $a \le b$ if and only if $a \land \neg b = 0$.
\end{lemma}

\begin{lemma}[\cite{givant2008introduction}] \label{lemma:measure_and_order}
  Let $m\colon \mathbf{B} \to \mathbb{R}_{\ge 0}$ be a measure. Then for all $a,
  b \in \mathbf{B}$, if $a \le b$, then $m(a) \le m(b)$.
\end{lemma}

\begin{definition}[Operations on functions]
  Let $A\colon 2^X \to \mathbb{R}_{\ge 0}$ and $B\colon 2^Y \to \mathbb{R}_{\ge
    0}$ be Boolean functions, $\alpha \in \mathbb{R}_{\ge 0}$, and $x \in X$. We
  define the following operations:
  \begin{description}
  \item[Addition:] $A+B$ is a function $A+B\colon 2^{X \cup Y} \to
    \mathbb{R}_{\ge 0}$ such that
    \[
      (A+B)(\tau) = A(\tau \cap X) + B(\tau \cap Y)
    \]
    for all $\tau \in 2^{X \cup Y}$.
  \item[Inverse:] $\overline{A}$ is a function $\overline{A}\colon 2^X \to
    \mathbb{R}_{\ge 0}$ such that
    \[
      \overline{A}(\tau) = 1 - A(\tau)
    \]
    for all $\tau \in 2^X$.
  \item[Multiplication:] $A \cdot B$ is a function $A \cdot B\colon 2^{X \cup Y}
    \to \mathbb{R}_{\ge 0}$ such that
    \[
      (A \cdot B)(\tau) = A(\tau \cap X) \cdot B(\tau \cap Y)
    \]
    for all $\tau \in 2^{X \cup Y}$.
  \item[Scalar multiplication:] $\alpha A$ is a function $\alpha A\colon 2^X \to
    \mathbb{R}_{\ge 0}$ such that
    \[
      (\alpha A)(\tau) = \alpha \cdot A(\tau)
    \]
    for all $\tau \in 2^X$.
  \item[Projection:] $\exists_xA$ is a function $\exists_xA\colon 2^{X \setminus
      \{ x \}} \to \mathbb{R}_{\ge 0}$ such that
    \[
      (\exists_xA)(\tau) = A(\tau) + A(\tau \cup \{ x \})
    \]
    for all $\tau \in 2^{X \setminus \{x \}}$.
  \end{description}
\end{definition}

\begin{observation}
  Let $\mathcal{V} = \{ A\colon 2^X \to \mathbb{R}_{\ge 0} \mid X \subseteq U
  \}$. Then $\mathcal{V}$ is a semi-vector space with three additional
  operations: inverse, (non-scalar) multiplication, and projection.
  Specifically, note that both addition and multiplication are both associative
  and commutative.
\end{observation}

\begin{definition}[Special functions]
  \phantom{}
  \begin{itemize}
  \item unit $1\colon 2^\emptyset \to \mathbb{R}_{\ge 0}$, $1(\tau) = 1$.
  \item zero $0\colon 2^\emptyset \to \mathbb{R}_{\ge 0}$, $0(\tau) = 0$.
  \item constant $[a]\colon 2^{\{a\}} \to \mathbb{R}_{\ge 0}$,
    \[
      [a](\tau) =
      \begin{cases}
        1 & \text{if } a \in \tau \\
        0 & \text{if } a \not\in \tau.
      \end{cases}
    \]
  \end{itemize}
\end{definition}

\begin{itemize}
\item[F2] Explain with examples: models $=$ elements [atoms] of algebra.
\item Be careful about mentioning ideals and quotients.
\end{itemize}

\begin{definition} \label{def:wmc}
  Let $U$ be an arbitrary set. Then
  \begin{itemize}
  \item a \emph{measure} is a function $M\colon 2^{2^U} \to \mathbb{R}_{\ge 0}$,
  \item a \emph{weight function} is a function $W\colon 2^U \to \mathbb{R}_{\ge
      0}$.
  \item a weight function is \emph{factored} if $W = \prod_{x \in U} W_x$ for
    some functions $W_x\colon 2^{\{x\}} \to \mathbb{R}_{\ge 0}$.
  \item every weight function induces a measure:
    \[
      M_W(x) = \begin{cases}
        0 & \text{if } x = \bot \\
        W(u) & \text{if } x = \{ u \} \\
        \sum_{\{u\} \le x} W(u) & \text{otherwise.}
      \end{cases}
    \]
    The process of calculating the value of $M_W(x)$ for some $x \in 2^{2^U}$
    with a given definition of $W$ is known as \emph{weighted model counting}.
  \item A measure $M\colon 2^{2^U} \to \mathbb{R}_{\ge 0}$ is
    \emph{factorable} if there exists a factored weight function $W\colon 2^U
    \to \mathbb{R}_{\ge 0}$ that induces $M$.
  \end{itemize}
\end{definition}

\begin{example} \label{example:construction}
  Let $\mathcal{L}$ be a propositional logic with $p$ and $q$ as its only atoms.
  Then $L = \{ p, q, \neg p, \neg q \}$ is its set of literals. Let $w : L \to
  \mathbb{R}_{\ge 0}$ be the \emph{weight function} defined by
  \begin{align*}
    w(p) = 0.3, \\
    w(\neg p) = 0.7, \\
    w(q) = 0.2, \\
    w(\neg q) = 0.8.
  \end{align*}
  Let $\Delta$ be a theory in $\mathcal{L}$ with a sole axiom $p$. Then
  $\Delta$ has two models, i.e., $\{ p, q \}$ and $\{ p, \neg q \}$. The
  \emph{weighted model count} (WMC) \cite{DBLP:journals/ai/ChaviraD08} of $\Delta$ is
  then
  \[
    \sum_{\omega \models \Delta} \prod_{\omega \models l} w(l) =
    w(p)w(q) + w(p)w(\neg q) = 0.3.
  \]

  The corresponding BA $B(\Delta)$ can then be constructed as a
  Lindenbaum-Tarski algebra. Alternatively, one can first construct the free
  BA generated by the set $\{ p, q \}$ and then take a quotient with respect to
  either the filter generated by $p$ or the ideal\footnote{More details on these
    concepts can be found in many books on BAs
    \cite{givant2008introduction,koppelberg1989handbook}.} generated by $\neg
  p$.

  Each element of $B(\mathcal{L})$ can also be seen as a subset of the set of
  all models of $\mathcal{L}$, with $0$ representing $\emptyset$, $1$
  representing the set of all (four) models, each atom representing a single
  model, and each edge going upward representing a subset relation. Thus,
  the Boolean-algebraic way of calculating the WMC of $\Delta$ consists of:
  \begin{enumerate}
  \item Identifying an element $a \in B(\mathcal{L})$ that corresponds to
    $\Delta$.
  \item Finding all atoms of $B(\mathcal{L})$ that are `dominated' by $a$
    according to the partial order.
  \item Using $w$ to calculate the weight of each such atom.
  \item Adding the weights of these atoms.
  \end{enumerate}
  This motivates the following definition of WMC generalised to BAs.
\end{example}
\todo[inline,caption={}]{
  \begin{itemize}
  \item Why is Step 1 always possible?
  \item Clarify what $B(L)$ means and whether $B(\Delta)$ is even necessary.
  \item Find a reference for the set/subset thing.
  \end{itemize}
}

Given a theory $\Delta$ in a logic $\mathcal{L}$, the usual way of using WMC to
compute the probability of a query $q$ is
\cite{DBLP:conf/uai/Belle17,DBLP:conf/aaai/SangBK05}
\[
  \Pr_{\Delta, w}(q) = \frac{\WMC_w(\Delta \land q)}{\WMC_w(\Delta)}.
\]
In our algebraic formulation, this can be computed in two different ways:
\begin{itemize}
\item as $\frac{\WMC_w(\Delta \land q)}{\WMC_w(\Delta)}$ in $B(\mathcal{L})$,
\item and as $\nWMC_w([q])$ in $B(\Delta)$.
\end{itemize}
But how does the measure defined on $B(\mathcal{L})$ transfer to $B(\Delta)$?

@@

\todo[inline]{This theorem needs a special case for zero weights.}
\begin{theorem}
  A measure $M\colon 2^{2^U} \to \mathbb{R}_{\ge 0}$ is factorable if and only
  if
  \begin{equation} \label{eq:wmccondition}
  M(u \land v) = M(u)M(v)
  \end{equation}
  for all distinct $u, v \in U \cup \{ \neg w \mid w \in U \}$ such that $u \ne
  \neg v$.
\end{theorem}
\begin{proof}
  ($\Leftarrow$) For each $x \in U$, let $W_x\colon 2^{\{x\}} \to
  \mathbb{R}_{\ge 0}$ be defined by $W_x(\{ x \}) = M(x)$ and $W_x(\emptyset) =
  M(\neg x)$. Let $M_W$ be the measure induced by
  \[
    W = \prod_{x \in U} W_x.
  \]
  We will show that $M = M_W$. First, note that $M_w(\bot) = 0 = M(\bot)$ by the
  definitions of both $M_w$ and $M$. Second, let
  \begin{equation} \label{eq:def_of_a}
    a = \bigwedge_{u \in U} a_u
  \end{equation}
  be an atom in $2^{2^U}$ such that $a_u \in \{ u, \neg u \}$ for all $u \in U$.
  Then
  \[
    M_W(a) = \prod_{u \in U} W_u(a_u) = \prod_{u \in U} M(a_u) = M
    \left(\bigwedge_{u \in U} a_u \right) = M(a)
  \] % TODO: by what?
  by \cref{def:wmc,eq:wmccondition,eq:def_of_a}. Finally, note that if $M_W$ and
  $M$ agree on all atoms, then they must also agree on all other non-zero
  elements of the Boolean algebra.

@@

Given this requirement for independence, a well-known way to represent
probability distributions that do not consist entirely of independent variables
is by adding more literals \cite{DBLP:journals/ai/ChaviraD08}, i.e., extending
the set $L$ covered by the WMC weight function $w\colon L \to \mathbb{R}_{\ge
  0}$. More precisely, we are given the left-hand column in
\[
  \begin{tikzcd}
    \textcolor{red}{\mathbb{R}_{\ge 0}} & & \\
    \textcolor{red}{\mathbf{B}} \arrow[red]{u}{m} \ar[r,hookrightarrow,"\iota"]
    & \mathbf{B'} \arrow{lu}[swap]{m'} & \\
    \textcolor{red}{L} \ar[u,red,hookrightarrow] \ar[r,hookrightarrow] & L'
    \ar[u,hookrightarrow] \arrow{r}{w} & \mathbb{R}_{\ge 0}
  \end{tikzcd}
\]
and construct the remaining part in such a way that the triangle commutes.

\todo[inline]{Must quotient the BA w.r.t. some rules.}

@@

\begin{itemize}
\item \texttt{cd05} relaxes the encoding so much that extra models become
  possible. They are supposed to be filtered out by the algorithm, but mine
  can't do that because it doesn't deal with models. Same for \texttt{cd06}
  because it's based on \texttt{cd05}.
\item \texttt{sbk05} uses my trick with dividing probabilities. That could
  explain small inaccuracies in its answers.
\item Encodings:
  \begin{itemize}
  \item \texttt{d02} \cite{DBLP:conf/kr/Darwiche02}
  \item \texttt{sbk05} \cite{DBLP:conf/aaai/SangBK05}
  \item \texttt{cd05} \cite{DBLP:conf/ijcai/ChaviraD05}
  \item \texttt{cd06} \cite{DBLP:conf/sat/ChaviraD06} (supposed to be the best)
  \item \texttt{db20} (mine)
  \end{itemize}
\end{itemize}

@@

\todo[inline]{Calculate numVariables/numClauses (or the other way around) for
  each instance and plot this ratio vs runtime (for each encoding, or at least
  mine and D02)}

>>>>

\section{Boolean Algebras and Power Sets}

\todo[inline]{
  Notation: make up my mind about $a, b$ vs. $x, y$ and stick to it (maybe $x,
  y$?).
}

\begin{table}
  \centering
  \caption{A comparison of Boolean-algebraic (BA) and set-theoretic (ST)
    concepts for $2^X$ for some set $X$}
  \label{tbl:notation}
  \begin{tabular}{lccl}
    \toprule
    BA name & BA symbol & ST symbol & ST name \\
    \midrule
    bottom & $\bot$ & $\emptyset$ & empty set \\
    top & $\top$ & $X$ & \\
    meet, and & $\land$ & $\cap$ & intersection \\
    join, or & $\lor$ & $\cup$ & union \\
    complement, not & $\neg$ & $^c$ & complement \\
            & $\le$ & $\subseteq$ & subset relation, set inclusion \\
    atom & & & singleton, unit set \\
    \bottomrule
  \end{tabular}
\end{table}

Let $X$ be a set and let $2^X$ be its power set. We can equivalently interpret
$2^X$ as a Boolean algebra. See \cref{tbl:notation} for a summary of the
differences in terminology and notation. We will use both.

\begin{definition}[Operations on functions]
  Let $A\colon 2^X \to \mathbb{R}_{\ge 0}$ and $B\colon 2^Y \to \mathbb{R}_{\ge
    0}$ be arbitrary functions, $\alpha \in \mathbb{R}_{\ge 0}$, and $x \in X$.
  We define the following operations:
  \begin{description}
  \item[Addition:] $A+B$ is a function $A+B\colon 2^{X \cup Y} \to
    \mathbb{R}_{\ge 0}$ such that
    \[
      (A+B)(\tau) = A(\tau \cap X) + B(\tau \cap Y)
    \]
    for all $\tau \in 2^{X \cup Y}$.
  \item[Inverse:] $\overline{A}$ is a function $\overline{A}\colon 2^X \to
    \mathbb{R}_{\ge 0}$ such that
    \[
      \overline{A}(\tau) = 1 - A(\tau)
    \]
    for all $\tau \in 2^X$.
  \item[Multiplication:] $A \cdot B$ is a function $A \cdot B\colon 2^{X \cup Y}
    \to \mathbb{R}_{\ge 0}$ such that
    \[
      (A \cdot B)(\tau) = A(\tau \cap X) \cdot B(\tau \cap Y)
    \]
    for all $\tau \in 2^{X \cup Y}$.
  \item[Scalar multiplication:] $\alpha A$ is a function $\alpha A\colon 2^X \to
    \mathbb{R}_{\ge 0}$ such that
    \[
      (\alpha A)(\tau) = \alpha \cdot A(\tau)
    \]
    for all $\tau \in 2^X$.
  \item[Projection:] $\exists_xA$ is a function $\exists_xA\colon 2^{X \setminus
      \{ x \}} \to \mathbb{R}_{\ge 0}$ such that
    \[
      (\exists_xA)(\tau) = A(\tau) + A(\tau \cup \{ x \})
    \]
    for all $\tau \in 2^{X \setminus \{x \}}$.
  \end{description}
\end{definition}

\begin{observation}
  Let $U$ be a set, and $\mathcal{V} = \{ A\colon 2^X \to \mathbb{R}_{\ge 0}
  \mid X \subseteq U \}$. Then $\mathcal{V}$ is a semi-vector space with three
  additional operations: inverse, (non-scalar) multiplication, and projection.
  Specifically, note that both addition and multiplication are both associative
  and commutative.
\end{observation}

\begin{definition}[Special functions]
  \phantom{}
  \begin{itemize}
  \item unit $1\colon 2^\emptyset \to \mathbb{R}_{\ge 0}$, $1(\emptyset) = 1$.
  \item zero $0\colon 2^\emptyset \to \mathbb{R}_{\ge 0}$, $0(\emptyset) = 0$.
  \item constant $[a]\colon 2^{\{a\}} \to \mathbb{R}_{\ge 0}$, $[a](\emptyset) =
    0$, $[a](\{a\}) = 1$.
  \end{itemize}
\end{definition}

\begin{itemize}
\item Describe \cref{tbl:notation_example} as an example.
\item[F] Feedback: explain with examples: models $=$ atoms of algebra, formulas
  $=$ all elements.
\end{itemize}

\begin{definition} \label{def:wmc}
  Let $U$ be a set.
  \begin{itemize}
  \item A \emph{measure} is a function $M\colon 2^{2^U} \to \mathbb{R}_{\ge 0}$
    such that $M(\bot) = 0$ and
    \[
      M(a \lor b) = M(a) + M(b)
    \]
    for all $a, b \in 2^{2^U}$ whenever $a \land b = \bot$.
  \item A \emph{weight function} is a function $W\colon 2^U \to \mathbb{R}_{\ge
      0}$.
  \item A weight function is \emph{factored} if $W = \prod_{x \in U} W_x$ for
    some functions $W_x\colon 2^{\{x\}} \to \mathbb{R}_{\ge 0}$.
  \item A measure $M\colon 2^{2^U} \to \mathbb{R}_{\ge 0}$ is
    \emph{factorable} if there exists a factored weight function $W\colon 2^U
    \to \mathbb{R}_{\ge 0}$ that induces $M$.
  \end{itemize}
\end{definition}

\begin{proposition}
  Every weight function induces a measure:
  \[
    M_W(x) = \begin{cases}
      0 & \text{if } x = \bot \\
      W(u) & \text{if } x = \{ u \} \\
      \sum_{\{u\} \le x} W(u) & \text{otherwise.}
    \end{cases}
  \]
\end{proposition}
The process of calculating the value of $M_W(x)$ for some $x \in 2^{2^U}$ with a
given definition of $W$ is known as \emph{weighted model counting}.
\begin{proof}
  \todo[inline]{Prove that $M_W$ satisfies the definition of a measure.}
\end{proof}

@@

\begin{example}[Relation to the classical view of WMC] \label{example:construction}
  Let $\mathcal{L}$ be a propositional logic with a set of atoms $U = \{ p, q
  \}$. Let $w : \{ p, q, \neg p, \neg q \} \to \mathbb{R}_{\ge 0}$ be the
  \emph{weight function} defined by
  \begin{align*}
    w(p) = 0.3, \quad w(\neg p) = 0.7, \quad w(q) = 0.2, \quad w(\neg q) = 0.8.
  \end{align*}
  Let $\Delta$ be a theory in $\mathcal{L}$ with a sole axiom $p$. Then
  $\Delta$ has two models, i.e., $\{ p, q \}$ and $\{ p, \neg q \}$. The
  \emph{weighted model count} (WMC) \cite{DBLP:journals/ai/ChaviraD08} of
  $\Delta$ is then
  \begin{equation} \label{eq:wmc_example}
    \sum_{\omega \models \Delta} \prod_{\omega \models l} w(l) =
    w(p)w(q) + w(p)w(\neg q) = 0.3.
  \end{equation}

  Alternatively, we can define $W_p\colon 2^{\{p\}} \to \mathbb{R}_{\ge 0}$ as
  \[
    W_p(\{ p \}) = 0.3, \quad W_p(\emptyset) = 0.7
  \]
  and $W_q\colon 2^{\{q\}} \to \mathbb{R}_{\ge 0}$ as
  \[
    W_q(\{ q \}) = 0.2, \quad W_q(\emptyset) = 0.8.
  \]
  Let $M$ be the measure on $2^{2^U}$ induced by $W = W_p \cdot W_q$. Then,
  equivalently to \cref{eq:wmc_example}, we can write
  \[
    M(p) = W(\{ p, q \}) + W(\{ p, \neg q \}) = W_p(\{p\})W_q(\{q\}) +
    W_p(\{p\})W_q(\{\neg q\}) = 0.3.
  \]
\end{example}

For the rest of the paper, we let $U$ be the set of (logical) atoms. We use
set-theoretic notation for $2^U$ and Boolean-algebraic notation for $2^{2^U}$,
except for (Boolean) atoms in $2^{2^U}$ that are denoted as $\{x\}$ for some
model $x \in 2^U$.

\todo[inline]{Include this in the example.}
Given a theory $\Delta$ in a logic $\mathcal{L}$, the usual way of using WMC to
compute the probability of a query $q$ is
\cite{DBLP:conf/uai/Belle17,DBLP:conf/aaai/SangBK05}
\[
  \Pr_{\Delta, w}(q) = \frac{\WMC_w(\Delta \land q)}{\WMC_w(\Delta)}.
\]
In our algebraic formulation, this can be computed...

@@

\todo[inline]{This theorem needs a special case for zero weights.}
\begin{theorem}
  A measure $M\colon 2^{2^U} \to \mathbb{R}_{\ge 0}$ is factorable if and only
  if
  \begin{equation} \label{eq:wmccondition}
  M(u \land v) = M(u)M(v)
  \end{equation}
  for all distinct $u, v \in U \cup \{ \neg w \mid w \in U \}$ such that $u \ne
  \neg v$.
\end{theorem}
\begin{proof}
  ($\Leftarrow$) For each $x \in U$, let $W_x\colon 2^{\{x\}} \to
  \mathbb{R}_{\ge 0}$ be defined by $W_x(\{ x \}) = M(x)$ and $W_x(\emptyset) =
  M(\neg x)$. Let $M_W$ be the measure induced by
  \[
    W = \prod_{x \in U} W_x.
  \]
  We will show that $M = M_W$. First, note that $M_w(\bot) = 0 = M(\bot)$ by the
  definitions of both $M_w$ and $M$. Second, let
  \begin{equation} \label{eq:def_of_a}
    a = \bigwedge_{u \in U} a_u
  \end{equation}
  be an atom in $2^{2^U}$ such that $a_u \in \{ u, \neg u \}$ for all $u \in U$.
  Then
  \[
    M_W(a) = \prod_{u \in U} W_u(a_u) = \prod_{u \in U} M(a_u) = M
    \left(\bigwedge_{u \in U} a_u \right) = M(a)
  \]
  \todo{by what?}
  by \cref{def:wmc,eq:wmccondition,eq:def_of_a}. Finally, note that if $M_W$ and
  $M$ agree on all atoms, then they must also agree on all other non-zero
  elements of the Boolean algebra.

@@

@@

\begin{itemize}
\item Encodings:
  \begin{itemize}
  \item \texttt{d02} \cite{DBLP:conf/kr/Darwiche02}
  \item \texttt{sbk05} \cite{DBLP:conf/aaai/SangBK05}
  \item \texttt{cd05} \cite{DBLP:conf/ijcai/ChaviraD05}
  \item \texttt{cd06} \cite{DBLP:conf/sat/ChaviraD06} (supposed to be the best)
  \item \texttt{db20} (mine)
  \end{itemize}
\item \texttt{cd05} relaxes the encoding so much that extra models become
  possible. They are supposed to be filtered out by the algorithm, but mine
  can't do that because it doesn't deal with models. Same for \texttt{cd06}
  because it's based on \texttt{cd05}.
\item \texttt{sbk05} uses my trick with dividing probabilities. That could
  explain small inaccuracies in its answers.
\end{itemize}

@@

\todo[inline]{Calculate numVariables/numClauses (or the other way around) for
  each instance and plot this ratio vs runtime (for each encoding, or at least
  mine and D02). The new CP paper kind of beat me to it...}
